---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# resamplr

[![Travis-CI Build Status](https://travis-ci.org/jrnold/resamplr.svg?branch=master)](https://travis-ci.org/jrnold/resamplr)
[![codecov](https://codecov.io/gh/jrnold/resamplr/branch/master/graph/badge.svg)](https://codecov.io/gh/jrnold/resamplr)

The **resamplr** package provides functions that implement resampling methods including the bootstrap, jackknife, random test/train sets, k-fold cross-validation, leave-one-out and leave-p-out cross-validation, time-series cross validation, time-series k-fold cross validation, permutations, rolling windows.
These functions generate data frames with `resample` objects that work with the modelling pipeline of [modelr](https://github.com/hadley/modelr) and the [tidyverse](http://tidyverse.org/).


## Installation

**resamplr** is not on CRAN. You can install the 
development version with
``` r
# install.packages("devtools")
devtools::install_github("jrnold/resamplr")
```

## Main Features

The **resamplr** package includes functions to generate data frames of 
lazy resample objects, as introduced in the [tidyverse](http://tidyverse.org/) [modelr](https://github.com/hadley/modelr) package. The `resample` class
stores the a "pointer" to the original dataset and a vector of row indices.
The object can be coerced to a dataframe with `as.data.frame` and the row indices with `as.integer`.

```{r}
library("modelr")
library("resamplr")
rs <- resample(mtcars, 1:10)
as.data.frame(rs)
as.integer(rs)
```

While the **modelr** package contains a few functions with resampling methods (`crossv_kfold`, `crossv_mc`, and `bootstrap`), the **resamplr** package implements many more resampling methods including the following: 

- boostrap

    - bootstrap (weighted, Bayesian): `bootstrap`
    - balanced bootstrap: `balanced_bootstrap`
    - time-series bootstrap: `tsbootstrap`

- cross-validation

    - test-training pairs: `holdout_n`, `holdout_frac`
    - k-fold cross-validation: `crossv_kfold`
    - time-series cross-validation: `crossv_ts`
    - leave-one-out and leave-p-out cross-validation: `crossv_lpo`, `crossv_loo`
    - time-series k-fold cross-validation: `crossv_tskfold`

- jackknife: `jackknife`
- permutations: `permute`
- rolling windows: `roll`
