---
title: "The resamplr package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Examples}
  %\VignetteEncoding{UTF-8}
---

This vignette contains some examples of cross-validation and bootstrapping with **resampler**.

## Cross Validation

These examples are taken from the examples in `cv.glm` in the **boot** package.

Calculate leave-one-out and 6-fold cross-validation prediction error for a regression of mammal brain size on body size using the `mammals` data set. This 
will use RMSE as the cost function.
```{r}
library("resamplr")
data(mammals, package = "MASS")
mammals_cvloo <- crossv_loo(mammals)
mammals_cv6 <- crossv_kfold(mammals, k = 6)

mammals_err <- function(train, test) {
  mod <- glm(log(brain) ~ log(body), data = as.data.frame(train))
  modelr::rmse(mod, as.data.frame(test))
}

map2_dbl(mammals_cvloo$train, mammals_cvloo$test, 
         mammals_err) %>%
  mean()

map2_dbl(mammals_cv6$train, mammals_cv6$test, 
         mammals_err) %>%
  mean()

```

Consider a regression of whether prostate cancer had spread to lymph nodes (`r`) in prostate cancer patients on several predictors.

We will calculate the out-of-sample fit using  leave-one-out cross validation and and 11-fold cross-validation prediction error for the `nodal` data set.  
Since it a binary outcome, we'll use the proportion classified correctly,
$$
\frac{1}{n} \sum I(\vert y_i - \hat{p}_i \vert > 0),
$$
as a measure of fit.
```{r}
nodal_err <- function(train, test) {
  mod <- glm(r ~ stage + xray + acid, binomial, data = as.data.frame(train))  
  test <- as.data.frame(test)
  p <- predict(mod, newdata = test, type = "response")
  mean(abs(test$r - p) > 0.5)
}
```
The expected fit from LOO-CV,
```{r}
nodal_cvloo <- crossv_loo(nodal)
map2_dbl(nodal_cvloo$train, nodal_cvloo$test, nodal_err) %>%
  mean()
```
and from 11-fold cross-validation,
```{r}
nodal_cv11 <- crossv_kfold(nodal, 11)
map2_dbl(nodal_cv11$train, nodal_cv11$test, nodal_err) %>%
  mean()
```


## Bootstrap

The examples are taken from the examples in the `boot` function of the **boot** package.

This is an ordinary bootstrap of the ratio of means using the `city` data
```{r}
bootstrap(city, k = 999) %>%
  mutate(ratio_means = map_dbl(sample, function(d) {
    d <- as.data.frame(d)
    mean(d$x) / mean(d$u)
  })) %>%
  summarise_at(vars(ratio_means), funs(mean, sd))
```

A stratified bootstrap uses the `bootstrap` function, but requires a `grouped_df` object as input.
The method `bootstrap.grouped_df` can resample groups (`groups = TRUE`), within groups (`stratify = TRUE`) or both. The default is a clustered bootstrap, resampling groups, but not rows within groups (`groups = TRUE, stratify = FALSE`).

In this example we will look at the difference of means between the final two series in the `gravity` data.
```{r}
gravity %>%
  filter(series %in% c("7", "8")) %>%
  group_by(series) %>%
  bootstrap(k = 999, stratify = TRUE, groups = FALSE) %>%
  mutate(diff_means = map_dbl(sample, function(d) {
    as.data.frame(d) %>%
      group_by(series) %>%
      summarise(g = mean(g)) %>%
      summarise(diff_means = base::diff(g)) %>%
      `[[`("diff_means")
  })) %>%
  summarise_at(vars(diff_means), funs(mean, sd))
```

